Cover letter for the original IJRR submission

### 2017-12-12 review_tro_2/reviewer_response.tex

\quot{I found few typos, but I believe that these would be removed in the
final editing process. 
The issues raised above are not essentia to the quality of the
contribution, but you can consider addressing these as an attempt to
improve the paper. }
\as{Thanks again for the comment. We made a last pass on the paper and indeed found a few remaining typos (negligeable -> negligible, implicitely -> implicitly, Euclidian -> Euclidean, travelled -> traveled, convervative -> conservative). More importantly we believe that we addressed all the remaining comments of the reviewer and hope that this will further improve the paper.}
\end{document}

### 2017-12-12 body/appendix_roms.tex
r2 typos

To generate a volume $W^k$, we proceed as follows:
\begin{enumerate}
\item Generate randomly $N$ valid limb configurations for $R^k$, for $N$ really large (say $100000$);
\item For each configuration, store the 3D position of the end effector joint relatively to the root of $R^k$; then compute the convex hull of the resulting point cloud;
\item The resulting polytope can contain a very large number of faces. A last step is thus to simplify it with the blender decimate tool (\url{http://wiki.blender.org/index.php/Doc:2.4/Manual/Modifiers/Generate/Decimate}). This tool removes a user-defined amount of vertices (and faces) of the polytope, thus resulting
in a convervative approximation of the original shape. For HRP-2 we apply the operator with a ratio of $0.06$, resulting in a polytope of 38 faces for the arms and the legs.
\end{enumerate}

>>>>

To generate a volume $W^k$, we proceed as follows:
\begin{enumerate}
\item Generate randomly $N$ valid limb configurations for $R^k$, for $N$ really large (say $100000$);
\item For each configuration, store the 3D position of the end effector joint relatively to the root of $R^k$; then compute the convex hull of the resulting point cloud;
\item The resulting polytope can contain a very large number of faces. A last step is thus to simplify it with the blender decimate tool (\url{http://wiki.blender.org/index.php/Doc:2.4/Manual/Modifiers/Generate/Decimate}). This tool removes a user-defined amount of vertices (and faces) of the polytope, thus resulting
in a conservative approximation of the original shape. For HRP-2 we apply the operator with a ratio of $0.06$, resulting in a polytope of 38 faces for the arms and the legs.
\end{enumerate}

### 2017-12-12 body/contact.tex
r2 typos

\subsection{Definition of a contact sequence}
In previous contributions~\citep{DBLP:conf/iser/EscandeKMG08}, a contact plan is defined as a sequence of quasi-static equilibrium configurations
for each contact phase. For instance, a walk cycle would be described by three key configurations: a double-support configuration, a single-support configuration (a contact is broken), and another double-support configuration (a contact is created). 
Our definition of contact plan differs: between two consecutive configurations we allow both a contact break and a contact creation---if they are on the same effector. 
In the previous example, our contact plan would simply consist of the two double-support configurations. 
%However, if the contact broken and the contact created sequentially are not on the same effector, our planner outputs two distinct states.
This representation is sufficient to describe all the contact phases, because the single support phase is implicitely described. Furthermore it removes the need to compute a single-support quasi-static configuration as in the example. Indeed, there might be a case where no quasi-static solution exists for the single support phase (because of the environment), but
there exists a dynamic motion connecting the two double support states. Such motion will be computed by our framework, because the quasi-static constraint is only required at the contact planning phase; as shown in the companion video, and explained in Appendix~\ref{app:optim}, our framework is able to produce dynamic motions.

@@

where $\mathbf{q}^0_{0}$ and $\mathbf{q}^0_{j-1}$ are the start and goal configurations. %To ensure continuity in the contact transition phases,
$j$ depends on a user-defined variable, called the discretization step. It corresponds to the ratio between the length of the path $\mathbf{q}^0(t)$\footnote{The length of the path is computed as the weighted 6D Euclidian distance
travelled along the it, with a weight of $0.7$ for the translation part, and $0.3$ for the orientation part.}, and the number
of configurations selected along it to create the contact configurations. 
Each root configuration of $\mathbf{Q}^0$ is then extended into a whole-body configuration such that:
\begin{itemize} 
\item At most one contact is not maintained (\textit{broken}) between two consecutive configurations.
\item At most one contact is added between two consecutive configurations.
\item Each configuration is in static equilibrium.
\item Each configuration is collision-free.
\end{itemize}

>>>>

\subsection{Definition of a contact sequence}
In previous contributions~\citep{DBLP:conf/iser/EscandeKMG08}, a contact plan is defined as a sequence of quasi-static equilibrium configurations
for each contact phase. For instance, a walk cycle would be described by three key configurations: a double-support configuration, a single-support configuration (a contact is broken), and another double-support configuration (a contact is created). 
Our definition of contact plan differs: between two consecutive configurations we allow both a contact break and a contact creation---if they are on the same effector. 
In the previous example, our contact plan would simply consist of the two double-support configurations. 
%However, if the contact broken and the contact created sequentially are not on the same effector, our planner outputs two distinct states.
This representation is sufficient to describe all the contact phases, because the single support phase is implicitly described. Furthermore it removes the need to compute a single-support quasi-static configuration as in the example. Indeed, there might be a case where no quasi-static solution exists for the single support phase (because of the environment), but
there exists a dynamic motion connecting the two double support states. Such motion will be computed by our framework, because the quasi-static constraint is only required at the contact planning phase; as shown in the companion video, and explained in Appendix~\ref{app:optim}, our framework is able to produce dynamic motions.

@@

where $\mathbf{q}^0_{0}$ and $\mathbf{q}^0_{j-1}$ are the start and goal configurations. %To ensure continuity in the contact transition phases,
$j$ depends on a user-defined variable, called the discretization step. It corresponds to the ratio between the length of the path $\mathbf{q}^0(t)$\footnote{The length of the path is computed as the weighted 6D Euclidean distance
traveled along the it, with a weight of $0.7$ for the translation part, and $0.3$ for the orientation part.}, and the number
of configurations selected along it to create the contact configurations. 
Each root configuration of $\mathbf{Q}^0$ is then extended into a whole-body configuration such that:
\begin{itemize} 
\item At most one contact is not maintained (\textit{broken}) between two consecutive configurations.
\item At most one contact is added between two consecutive configurations.
\item Each configuration is in static equilibrium.
\item Each configuration is collision-free.
\end{itemize}
